Wealth dynamics in the presence of network structure and primitive cooperation

### 2019-07-13 manuscript/verification.tex
Gini analysis and verification

\begin{figure}[hb]
\centering
\includegraphics[width=\columnwidth]{figures/giniHistory.png}
\caption{The simulated society's wealth inequality over time. (The same
simulation parameters were used as in Figures~\ref{fig:singleRun} and
\ref{fig:effectiveWealthSingleRun}, but this time with 500 agents.)}
\label{fig:giniHistory}
\end{figure}

>>>>

\begin{figure}[hb]
\centering
\includegraphics[width=\columnwidth]{figures/giniHistory.png}
\caption{The simulated society's wealth inequality over time. (The same
simulation parameters were used as in Figures~\ref{fig:singleRun} and
\ref{fig:effectiveWealthSingleRun}, but this time with 500 agents.) The light
blue band represents a bootstrapped 95\% confidence interval.}
\label{fig:giniHistory}
\end{figure}
The Gini index of the agent population as seen in the top graph is influenced by two distinct dynamics: loss/accumulation of wealth and the formation/death of proto-institutions. Over the course of Stage 1 and the beginning of Stage 3, this change in agent wealth is exclusively responsible for changes in the Gini index. As agents accumulate wealth over Stage 1 and 2, the size of wealth differentials shrinks relative to absolute agent wealth, leading to the declining Gini index. The opposite effect occurs during Stage 3 as agent starvation leads to the relative growth of these wealth differentials. The variability in starvation rates further contributes to the increasing Gini index.
In addition, the proto-institution formation and proto-institution death respectively, indicated by the bottom graph, influence the Gini index during Stage 2 and the end of Stage 3. As expected, the formation of proto-institutions during Stage 2 contributes to declining Gini index as the constituent agents of each proto-institution have equivalent wealth values and represent coalitions of perfect economic equality. Accordingly, the death of proto-institutions, beginning around Iteration 20, contributes to increase the Gini coefficient by removing the on the system’s inequality. 
Note: As the population size decreases over the starvation period the Gini index becomes increasingly unstable and susceptible to fluctuations in agent wealth.
